---
title: 'Sep 17 Synchronous Session'
author: 'Data Science for Biomedical Informatics (BMIN503/EPID600)'
output: 
  html_document:
    theme: cerulean
    highlight: pygments
---

***

### COVID in Philadelphia

1. Load data frames called `covid.jul` and `covid.aug` corresponding to covid test results reported by the Philadelphia Department of Public Health on July 7 and August 11, 2020 that are in files `phl_covid_tests_7.7.20.txt` and `phl_covid_tests_8.11.20.txt`, respectively.

```{r, eval = TRUE}
covid.jul <- read.table(file = "phl_covid_tests_7.7.20.txt", header = TRUE, sep = "\t", skip = 0, na.strings = NA, nrows = -1)
covid.aug <- read.table(file = "phl_covid_tests_8.11.20.txt", header = TRUE, sep = "\t", skip = 0, na.strings = NA, nrows = -1)
```

2. How many COVID-19 test results had been reported in Philadelphia by August 11? 
```{r, eval = TRUE}
total.count <- function(x){
  y <- sum(x$count)
  paste0("The total number of test results reported in Philadelphia is ", y)
}

total.count(covid.aug)
```

3. What zip code had the greatest number of positive tests by August 11?
```{r, eval = TRUE}
find.max.pos <- function(x){
  maxpos <- max(x$count[x$covid_status == "POS"])
  maxzip <- x[x$covid_status == "POS", ][which.max(x[x$covid_status == "POS", "count"]),"zip_code"]
  
  paste0("Zip code with most positive cases was ", maxzip, " with ", maxpos, " cases.")
}

find.max.pos(covid.aug)

```

4. Create a function `most.neg` that returns the zip code with the greatest number of negative tests along with that number as a data frame. Use the function to get this output for July 7 and Aug 11.
```{r, eval = TRUE}
most.neg <- function(x){
  maxneg <- max(x$count[x$covid_status == "NEG"])
  maxzip <- x[x$covid_status == "NEG", ][which.max(x[x$covid_status == "NEG", "count"]),"zip_code"]
  
  print(paste0("Zip code with most negative cases was ", maxzip, " with ", maxneg, " cases."))
  
  df <- data.frame(maxzip, maxneg)
  colnames(df) <- c("zip_code","count")
  return(df)
}

aug.df <- most.neg(covid.aug)
jul.df <- most.neg(covid.jul)
```


***